---
title: "Building Management <br> Reports using the <br> flexdashboard package"
subtitle: "PHI useR Group"
author: 'Alice Byers <br> Information Services Division <br>'
date: "25 February 2020 <br><br> Slides: https://github.com/alicebyers5/useR-presentation"
output:
  ioslides_presentation:
    widescreen: true
    css: my-theme.css
---

```{r setup, include = FALSE}
# Load packages required
library(knitr)

knitr::opts_chunk$set(echo = TRUE)

error_hook <- knitr::knit_hooks$get("error")
knitr::knit_hooks$set(error = function(x, options) {
  if (!is.null(n <- options$linewidth)) {
    x = knitr:::split_lines(x)
    if (any(nchar(x) > n)) x = strwrap(x, width = n)
    x = paste(x, collapse = '\n')
  }
  error_hook(x, options)
})
```


## Background and Motivation

- Quarterly management reports for [Dementia Post Diagnostic Support (PDS)](https://www.isdscotland.org/Health-Topics/Mental-Health/Dementia-Post-diagnostic-Support/) data

- SPSS used for data preparation and calculating measures

- Excel used to present data

- New data recording guidance prompted review of methodology and presentation of management reports


## Requirements

- Restricted access

- Universal file format

- User friendly format


## Why flexdashboard?

- Uses R Markdown to produce interactive dashboards

- No requirement for shiny server; can be produced as standalone html file

- The production process can be automated using R


## Some code

Text

```{r, message = FALSE}
library(testthat)

expect_equal(2 + 3, 5)
expect_error(sum(1, "two"))
```

Text

```{r, error = TRUE}
expect_lt(3, 2)
```


## Contact

### Alice Byers - Health & Social Care Team

Email - [alice.byers@nhs.net](mailto:alice.byers@nhs.net)

GitHub - [alicebyers5](https://github.com/alicebyers5)

